White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2016-07-17 papers/wdmerger_II/paper.tex
Fix an exponent

We have also added to \wdmerger\ the ability to use the 2D cylindrical ($R-z$)
coordinate system evolution in \castro. In this coordinate system, we align
the WDs along the $z$-axis (which is analogous to our $x$-axis in the Cartesian
evolution) at the usual distance, with the center of the WDs at $R = 0$. The
un-simulated $\phi$ dimension then would extend the WDs through a $2\pi$ revolution.
The nature of the axisymmetry inherent to the cylindrical coordinate system
means that we can only run head-on collisions with $b = 0$. The coarse grid
is the same resolution as the 3D case: the width of the $z$ axis is $1.024 \times 10^{10}$
cm and the width of the $R$ axis is $5.012 \times 10^{10}$ cm, with twice as
many zones along the $z$ axis as the $R$ axis so that the equal 400 km
resolution is maintained.

>>>>

We have also added to \wdmerger\ the ability to use the 2D cylindrical ($R-z$)
coordinate system evolution in \castro. In this coordinate system, we align
the WDs along the $z$-axis (which is analogous to our $x$-axis in the Cartesian
evolution) at the usual distance, with the center of the WDs at $R = 0$. The
un-simulated $\phi$ dimension then would extend the WDs through a $2\pi$ revolution.
The nature of the axisymmetry inherent to the cylindrical coordinate system
means that we can only run head-on collisions with $b = 0$. The coarse grid
is the same resolution as the 3D case: the width of the $z$ axis is $1.024 \times 10^{10}$
cm and the width of the $R$ axis is $5.012 \times 10^{9}$ cm, with twice as
many zones along the $z$ axis as the $R$ axis so that the equal 400 km
resolution is maintained.
